Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-03 main.tex
More related work comments

\item StkTokens: Skorstengaard, Devriese, Birkedal
\begin{itemize}
\item \url{https://arxiv.org/pdf/1811.02787.pdf}
\item \url{https://arxiv.org/pdf/1902.05283.pdf}
\item \url{http://cs.au.dk/~lask/papers/esop2018.pdf}
\item \url{https://dl.acm.org/doi/fullHtml/10.1145/3363519}
\end{itemize}

>>>>

\item Azevedo de Amorim's presentation of heap safety as a noninterference
property~\cite{DBLP:conf/post/AmorimHP18} was a key inspiration for our
definition of stack safety.  (Details...)

\item StkTokens: Skorstengaard, Devriese, Birkedal
\begin{itemize}
\item POPL \cite{skorstengaard2019stktokens}
\item tech report with proofs: \cite{skorstengaard2018stktokens}
\url{https://arxiv.org/pdf/1811.02787.pdf}
\item TR with proofs for ``Reasoning about a machine...'', Feb 2019:
\url{https://arxiv.org/pdf/1902.05283.pdf} 
\item \url{http://cs.au.dk/~lask/papers/esop2018.pdf}
\item Also: {\em Reasoning about a Machine with Local Capabilities: Provably
  Safe Stack and Return Pointer Management} \cite{10.1145/3363519}
\url{https://dl.acm.org/doi/fullHtml/10.1145/3363519}

\bcp{I'm nervous that these papers may be viewed as subsuming most of
  ours---in particular, their security property is formulated as a logical
  relation, i.e. a relational property!  We really need to dig into the
  details (which are unfortunately rather technical).}
\end{itemize}
